Mixture Models for Single-Cell Assays with Application to Vaccine Studies: Supplementary Materials

### 2013-05-16 MIMOSA.tex
Updated Supp figures

\begin{figure} %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics{TIKZFig3.eps}
%   \begin{tikzpicture} [auto, node distance=0cm]
%   \node at (0,0) (A) {
%\begin{tikzpicture}
%    \node [anchor=south west] at (0,0) (foo) {\includegraphics[width=0.45\columnwidth]{Figures/Sim_Onesided_ROC_5000.pdf}};
%    \begin{scope}[x={(foo.south east)},y={(foo.north west)}]
%        \node at (0,1) [font=\small\sffamily] {A} ;
%        \end{scope}
%    \end{tikzpicture}
%    };
%    \node [right=of A] (B) {
%    \begin{tikzpicture}
%    \node [anchor=south west] at (0,0) (bar) {\includegraphics[width=0.45\columnwidth]{Figures/Sim_Onesided_FDR_5000.pdf}};
%    \begin{scope}[x={(bar.south east)},y={(bar.north west)}]
%    \node at (0,1) [font=\small\sffamily] {B} ;
%    \end{scope}
%    \end{tikzpicture}
%    };
%        \node [below=of A] (C) {
%    \begin{tikzpicture}
%    \node [anchor=south west] at (0,0) (c) {\includegraphics[width=0.45\columnwidth]{Figures/Sim_Twosided_ROC_5000.pdf}};
%    \begin{scope}[x={(c.south east)},y={(c.north west)}]
%    \node at (0,1) [font=\small\sffamily] {C} ;
%    \end{scope}
%    \end{tikzpicture}
%    };
%    \node [right=of C] (D) {
%    \begin{tikzpicture}
%    \node [anchor=south west] at (0,0) (d) {\includegraphics[width=0.45\columnwidth]{Figures/Sim_Twosided_FDR_5000.pdf}};
%    \begin{scope}[x={(d.south east)},y={(d.north west)}]
%    \node at (0,1) [font=\small\sffamily] {D} ;
%    \end{scope}
%    \end{tikzpicture}
%    };
%
%\end{tikzpicture}
   \caption{Comparison of positivity detection methods on data simulated from the one-sided and two--sided models. Ten simulations were generated at an $N$ of 5,000 total counts using hyper-parameter estimates from real ICS data (IFN-$\gamma$ expressing CD4+ T-cells stimulated with ENV-1-PTEG from HVTN065) with a five-fold effect size between responder and non-responder components. A) Average ROC curve over the 10 simulated data sets (N=5,000), one--sided B) Average observed and nominal false discovery rate over 10 simulated data sets (N=5,000), one--sided. C) Average ROC curves, two--sided model. D) Average observed and nominal FDR, two--sided model. Curves are shown for MIMOSA, Fisher's exact test, the likelihood ratio test, and log fold-change. Results for MIMOSA fit to a model violating model assumptions, as well as other values of N are in Supplementary Figure 3. This figure appears in color in the electronic version of this article.}\label{fig:simulations}
\end{figure}

>>>>

\begin{figure} %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics{TIKZFig3.eps}
%   \begin{tikzpicture} [auto, node distance=0cm]
%   \node at (0,0) (A) {
%\begin{tikzpicture}
%    \node [anchor=south west] at (0,0) (foo) {\includegraphics[width=0.45\columnwidth]{Figures/Sim_Onesided_ROC_5000.pdf}};
%    \begin{scope}[x={(foo.south east)},y={(foo.north west)}]
%        \node at (0,1) [font=\small\sffamily] {A} ;
%        \end{scope}
%    \end{tikzpicture}
%    };
%    \node [right=of A] (B) {
%    \begin{tikzpicture}
%    \node [anchor=south west] at (0,0) (bar) {\includegraphics[width=0.45\columnwidth]{Figures/Sim_Onesided_FDR_5000.pdf}};
%    \begin{scope}[x={(bar.south east)},y={(bar.north west)}]
%    \node at (0,1) [font=\small\sffamily] {B} ;
%    \end{scope}
%    \end{tikzpicture}
%    };
%        \node [below=of A] (C) {
%    \begin{tikzpicture}
%    \node [anchor=south west] at (0,0) (c) {\includegraphics[width=0.45\columnwidth]{Figures/Sim_Twosided_ROC_5000.pdf}};
%    \begin{scope}[x={(c.south east)},y={(c.north west)}]
%    \node at (0,1) [font=\small\sffamily] {C} ;
%    \end{scope}
%    \end{tikzpicture}
%    };
%    \node [right=of C] (D) {
%    \begin{tikzpicture}
%    \node [anchor=south west] at (0,0) (d) {\includegraphics[width=0.45\columnwidth]{Figures/Sim_Twosided_FDR_5000.pdf}};
%    \begin{scope}[x={(d.south east)},y={(d.north west)}]
%    \node at (0,1) [font=\small\sffamily] {D} ;
%    \end{scope}
%    \end{tikzpicture}
%    };
%
%\end{tikzpicture}
   \caption{Comparison of positivity detection methods on data simulated from the one-sided and two--sided models. Ten simulations were generated at an $N$ of 50,000 total counts using hyper-parameter estimates from real ICS data (IFN-$\gamma$ expressing CD4+ T-cells stimulated with ENV-1-PTEG from HVTN065) with a five-fold effect size between responder and non-responder components. A) Average ROC curve over the 10 simulated data sets (N=50,000), one--sided B) Average observed and nominal false discovery rate over 10 simulated data sets (N=50,000), one--sided. C) Average ROC curves, two--sided model. D) Average observed and nominal FDR, two--sided model. Curves are shown for MIMOSA, Fisher's exact test, the likelihood ratio test, and log fold-change. Results for MIMOSA fit to a model violating model assumptions, as well as other values of N and I (number of subjects) are in Supplementary Figure 3. This figure appears in color in the electronic version of this article.}\label{fig:simulations}
\end{figure}

### 2013-05-16 SupplementaryMaterialMIMOSA.tex
Updated Supp figures

\begin{figure} %  figure placement: here, top, bottom, or page
   \centering
\begin{tikzpicture} [auto,node distance=0cm]
%\node at (0,0) (A) {
%\begin{tikzpicture}
%    \node[anchor=south west,inner sep=0] at (0,0) (a) {\includegraphics[width=0.4\columnwidth]{Figures/Sim_Twosided_ROC_5000.pdf}};
%    \begin{scope} [x={(a.south east)},y={(a.north west)}]
%        \node at (0,1) [font=\small\sffamily] {A} ;
%    \end{scope}
%    \end{tikzpicture}
%    };
%    \node [right=of A] (B) {
%    \begin{tikzpicture}
%    \node[anchor=south west, inner sep=0] at (0,0) (b) {\includegraphics[width=0.4\columnwidth]{Figures/Sim_Twosided_FDR_5000.pdf}};
%        \begin{scope} [x={(b.south east)},y={(b.north west)}]
%        \node at (0,1) [font=\small\sffamily] {B} ;
%        \end{scope}
%    \end{tikzpicture}
%    };
    \node at (0,0) (A) {
    \begin{tikzpicture}
     \node[anchor=south west,inner sep=0] at (0,0) (c) {\includegraphics[width=0.4\columnwidth]{Figures/Sim_Truncated_ROC_5000.pdf}};
         \begin{scope} [x={(c.south east)},y={(c.north west)}]
                 \node at (0,1) [font=\tiny\sffamily] {A} ;
	\end{scope}
     \end{tikzpicture}
     };
     \node [right=of A] (B) {
     \begin{tikzpicture}
    \node[anchor=south west, inner sep=0] at (0,0) (d) {\includegraphics[width=0.4\columnwidth]{Figures/Sim_Truncated_FDR_5000.pdf}};
        \begin{scope} [x={(d.south east)},y={(d.north west)}]
            \node at (0,1) [font=\tiny\sffamily] {B} ;
\end{scope}
    \end{tikzpicture}
    };
  \node [below=of A] (C) {
\begin{tikzpicture}
    \node[anchor=south west,inner sep=0] at (0,0) (e) {\includegraphics[width=0.4\columnwidth]{Figures/Sim_Truncated_ROC_1000.pdf}};
    \begin{scope} [x={(e.south east)},y={(e.north west)}]
        \node at (0,1) [font=\tiny\sffamily] {C} ;
    \end{scope}
    \end{tikzpicture}
    };
    \node [right=of C] (D) {
    \begin{tikzpicture}
    \node[anchor=south west, inner sep=0] at (0,0) (f) {\includegraphics[width=0.4\columnwidth]{Figures/Sim_Truncated_FDR_1000.pdf}};
        \begin{scope} [x={(f.south east)},y={(f.north west)}]
        \node at (0,1) [font=\tiny\sffamily] {D} ;
        \end{scope}
    \end{tikzpicture}
    };
%     \node [below=of C] (E) {
%     \begin{tikzpicture}
%      \node[anchor=south west,inner sep=0] at (0,0) (g) {\includegraphics[width=0.4\columnwidth]{Figures/Sim_Twosided_ROC_1000.pdf}};
%          \begin{scope} [x={(g.south east)},y={(g.north west)}]
%                  \node at (0,1) [font=\tiny\sffamily] {E} ;
% 	\end{scope}
%      \end{tikzpicture}
%      };
%      \node [right=of E] (F) {
%      \begin{tikzpicture}
%     \node[anchor=south west, inner sep=0] at (0,0) (h) {\includegraphics[width=0.4\columnwidth]{Figures/Sim_Twosided_FDR_1000.pdf}};
%         \begin{scope} [x={(h.south east)},y={(h.north west)}]
%             \node at (0,1) [font=\tiny\sffamily] {F} ;
% \end{scope}
%     \end{tikzpicture}
%     };
 \end{tikzpicture}
   \caption{Unconstrained MIMOSA model fit to data from a model
     violating model assumptions and to two-sided data with small
     counts. Data was simulated from a model where proportions were
     sampled from a truncated normal distribution over $[0,1]$ rather
     than a Beta distribution.  A) The average ROC from 10 simulation
     with N=5,000 events. B) The average observed and nominal FDR from
     10 simulations with N=5,000 events. C) Average ROC for N=1,000
     events D) Average observed and nominal FDR for N=1,000 events.
% MIMOSA fit to two-sided data were simulated from the standard model
% with N=1,000 events. E) Average ROC curves from 10 simulations and
% F) average observed vs nominal FDR from 10 simulations. This figure
% appears in color in the electronic version of this article.
}
   \label{webfig:simulations_trunc}
\end{figure}
\clearpage

>>>>

\begin{figure} %  figure placement: here, top, bottom, or page
   \centering
\begin{tikzpicture} [auto,node distance=0cm]
%\node at (0,0) (A) {
%\begin{tikzpicture}
%    \node[anchor=south west,inner sep=0] at (0,0) (a) {\includegraphics[width=0.4\columnwidth]{Figures/Sim_Twosided_ROC_5000.pdf}};
%    \begin{scope} [x={(a.south east)},y={(a.north west)}]
%        \node at (0,1) [font=\small\sffamily] {A} ;
%    \end{scope}
%    \end{tikzpicture}
%    };
%    \node [right=of A] (B) {
%    \begin{tikzpicture}
%    \node[anchor=south west, inner sep=0] at (0,0) (b) {\includegraphics[width=0.4\columnwidth]{Figures/Sim_Twosided_FDR_5000.pdf}};
%        \begin{scope} [x={(b.south east)},y={(b.north west)}]
%        \node at (0,1) [font=\small\sffamily] {B} ;
%        \end{scope}
%    \end{tikzpicture}
%    };
    \node at (0,0) (A) {
    \begin{tikzpicture}
     \node[anchor=south west,inner sep=0] at (0,0) (c) {\includegraphics[width=0.4\columnwidth]{Figures/Sim_Truncated_ROC_50K.pdf}};
         \begin{scope} [x={(c.south east)},y={(c.north west)}]
                 \node at (0,1) [font=\tiny\sffamily] {A} ;
	\end{scope}
     \end{tikzpicture}
     };
     \node [right=of A] (B) {
     \begin{tikzpicture}
    \node[anchor=south west, inner sep=0] at (0,0) (d) {\includegraphics[width=0.4\columnwidth]{Figures/Sim_Truncated_FDR_50K.pdf}};
        \begin{scope} [x={(d.south east)},y={(d.north west)}]
            \node at (0,1) [font=\tiny\sffamily] {B} ;
\end{scope}
    \end{tikzpicture}
    };
  \node [below=of A] (C) {
\begin{tikzpicture}
    \node[anchor=south west,inner sep=0] at (0,0) (e) {\includegraphics[width=0.4\columnwidth]{Figures/Sim_Truncated_ROC_10K.pdf}};
    \begin{scope} [x={(e.south east)},y={(e.north west)}]
        \node at (0,1) [font=\tiny\sffamily] {C} ;
    \end{scope}
    \end{tikzpicture}
    };
    \node [right=of C] (D) {
    \begin{tikzpicture}
    \node[anchor=south west, inner sep=0] at (0,0) (f) {\includegraphics[width=0.4\columnwidth]{Figures/Sim_Truncated_FDR_10K.pdf}};
        \begin{scope} [x={(f.south east)},y={(f.north west)}]
        \node at (0,1) [font=\tiny\sffamily] {D} ;
        \end{scope}
    \end{tikzpicture}
    };
%     \node [below=of C] (E) {
%     \begin{tikzpicture}
%      \node[anchor=south west,inner sep=0] at (0,0) (g) {\includegraphics[width=0.4\columnwidth]{Figures/Sim_Twosided_ROC_1000.pdf}};
%          \begin{scope} [x={(g.south east)},y={(g.north west)}]
%                  \node at (0,1) [font=\tiny\sffamily] {E} ;
% 	\end{scope}
%      \end{tikzpicture}
%      };
%      \node [right=of E] (F) {
%      \begin{tikzpicture}
%     \node[anchor=south west, inner sep=0] at (0,0) (h) {\includegraphics[width=0.4\columnwidth]{Figures/Sim_Twosided_FDR_1000.pdf}};
%         \begin{scope} [x={(h.south east)},y={(h.north west)}]
%             \node at (0,1) [font=\tiny\sffamily] {F} ;
% \end{scope}
%     \end{tikzpicture}
%     };
 \end{tikzpicture}
   \caption{Unconstrained MIMOSA model fit to data from a model
     violating model assumptions and to two-sided data with small
     counts. Data was simulated from a model where proportions were
     sampled from a truncated normal distribution over $[0,1]$ rather
     than a Beta distribution.  A) The average ROC from 10 simulation
     with N=5,000 events. B) The average observed and nominal FDR from
     10 simulations with N=5,000 events. C) Average ROC for N=1,000
     events D) Average observed and nominal FDR for N=1,000 events.
% MIMOSA fit to two-sided data were simulated from the standard model
% with N=1,000 events. E) Average ROC curves from 10 simulations and
% F) average observed vs nominal FDR from 10 simulations. This figure
% appears in color in the electronic version of this article.
}
   \label{webfig:simulations_trunc}
\end{figure}
\clearpage

### 2013-05-16 TIKZFig3.tex
Updated Supp figures

\documentclass{article}
\usepackage{tikz,amsmath,siunitx}
\usetikzlibrary{calc}
\usetikzlibrary{positioning}
\usetikzlibrary{arrows,snakes,backgrounds,patterns,matrix,shapes,fit,calc,shadows,plotmarks}
\usepackage[graphics,tightpage,active]{preview}
\PreviewEnvironment{tikzpicture}
\PreviewEnvironment{equation}
\PreviewEnvironment{equation*}
\newlength{\imagewidth}
\newlength{\imagescale}
\pagestyle{empty}
\thispagestyle{empty}
\begin{document}
  \begin{tikzpicture} [auto, node distance=0cm]
   \node at (0,0) (A) {
\begin{tikzpicture}
    \node [anchor=south west] at (0,0) (foo) {\includegraphics[width=0.5\columnwidth]{Figures/Sim_Onesided_ROC_5000.pdf}};
    \begin{scope}[x={(foo.south east)},y={(foo.north west)}]
        \node at (0,1) [font=\tiny\sffamily] {A} ;
        \end{scope}
    \end{tikzpicture}
    };
    \node [right=of A] (B) {
    \begin{tikzpicture}
    \node [anchor=south west] at (0,0) (bar) {\includegraphics[width=0.5\columnwidth]{Figures/Sim_Onesided_FDR_5000.pdf}};
    \begin{scope}[x={(bar.south east)},y={(bar.north west)}]
    \node at (0,1) [font=\tiny\sffamily] {B} ;
    \end{scope}
    \end{tikzpicture}
    };
        \node [below=of A] (C) {
    \begin{tikzpicture}
    \node [anchor=south west] at (0,0) (c) {\includegraphics[width=0.5\columnwidth]{Figures/Sim_Twosided_ROC_5000.pdf}};
    \begin{scope}[x={(c.south east)},y={(c.north west)}]
    \node at (0,1) [font=\tiny\sffamily] {C} ;
    \end{scope}
    \end{tikzpicture}
    };
    \node [right=of C] (D) {
    \begin{tikzpicture}
    \node [anchor=south west] at (0,0) (d) {\includegraphics[width=0.5\columnwidth]{Figures/Sim_Twosided_FDR_5000.pdf}};
    \begin{scope}[x={(d.south east)},y={(d.north west)}]
    \node at (0,1) [font=\tiny\sffamily] {D} ;
    \end{scope}
    \end{tikzpicture}
    };

>>>>

\documentclass{article}
\usepackage{tikz,amsmath,siunitx}
\usetikzlibrary{calc}
\usetikzlibrary{positioning}
\usetikzlibrary{arrows,snakes,backgrounds,patterns,matrix,shapes,fit,calc,shadows,plotmarks}
\usepackage[graphics,tightpage,active]{preview}
\PreviewEnvironment{tikzpicture}
\PreviewEnvironment{equation}
\PreviewEnvironment{equation*}
\newlength{\imagewidth}
\newlength{\imagescale}
\pagestyle{empty}
\thispagestyle{empty}
\begin{document}
  \begin{tikzpicture} [auto, node distance=0cm]
   \node at (0,0) (A) {
\begin{tikzpicture}
    \node [anchor=south west] at (0,0) (foo) {\includegraphics[width=0.5\columnwidth]{Figures/Sim_OneSided_ROC_50K.pdf}};
    \begin{scope}[x={(foo.south east)},y={(foo.north west)}]
        \node at (0,1) [font=\tiny\sffamily] {A} ;
        \end{scope}
    \end{tikzpicture}
    };
    \node [right=of A] (B) {
    \begin{tikzpicture}
    \node [anchor=south west] at (0,0) (bar) {\includegraphics[width=0.5\columnwidth]{Figures/Sim_OneSided_FDR_50K.pdf}};
    \begin{scope}[x={(bar.south east)},y={(bar.north west)}]
    \node at (0,1) [font=\tiny\sffamily] {B} ;
    \end{scope}
    \end{tikzpicture}
    };
        \node [below=of A] (C) {
    \begin{tikzpicture}
    \node [anchor=south west] at (0,0) (c) {\includegraphics[width=0.5\columnwidth]{Figures/Sim_TwoSided_ROC_50K.pdf}};
    \begin{scope}[x={(c.south east)},y={(c.north west)}]
    \node at (0,1) [font=\tiny\sffamily] {C} ;
    \end{scope}
    \end{tikzpicture}
    };
    \node [right=of C] (D) {
    \begin{tikzpicture}
    \node [anchor=south west] at (0,0) (d) {\includegraphics[width=0.5\columnwidth]{Figures/Sim_TwoSided_FDR_50K.pdf}};
    \begin{scope}[x={(d.south east)},y={(d.north west)}]
    \node at (0,1) [font=\tiny\sffamily] {D} ;
    \end{scope}
    \end{tikzpicture}
    };
